---
title: "Amniote life-history presentation"
author: "Sam Wolf"
date: "March 22, 2018"
output: 
  html_document:
    highlight: tango
    theme: journal
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r libraries, include=FALSE}
# Includes libraries
library(knitr)
library(tidyverse)

```

# Exploring the relationship of body size on lifestyle and productivity among Amniotes
##  How does body-size affect range distributions of amniotes?

Describe your question here

## Brief description of the methods

Using the Amniote life-history [database](http://www.esapubs.org/archive/ecol/E096/269/#data), I ...

```{r message=FALSE, warning=FALSE}
download.file("http://www.esapubs.org/archive/ecol/E096/269/Data_Files/Amniote_Range_Count_Aug_2015.csv
", "./Data/Amniote_Range_Count_Aug_2015.csv")

```
```{r}
# Read data
Amniote<-read.csv("./Data/Amniote_Range_Count_Aug_2015.csv")

# Explore data
# View(Amniote)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
